ManuscriptPURFits

### 2024-03-06 Code/Plots_PURFits.Rmd
Removed redundant packages, removed a lot of commented chunks

```{r load libraries, include=FALSE}
# libraries; Note check actual dependencies
library(tidyverse)
library(lubridate)
#library(stringr)
library(broom)
library(knitr)
library(zoo)
#library(AICcmodavg)
# library(RColorBrewer)
library(grid)
library(gridExtra)
# library(bookdown)
# library(glue)
library(egg)
# library(ggspectra)
# library(photobiologyWavebands)
# library(photobiology)
#library(ggpubr)
#library(ggh4x)
library(cowplot)
#library(jmv)
# library(pgirmess) # for the post hoc kruskalalmc test
#library(rcompanion) # for Scheirer-Ray-Hare non-parametric 2 way test, derived from Kruskal-Wallis
# library(FSA) # for Dunn test
#library(dunn.test)
# library(rstatix)
library(minpack.lm)

@@

library(photobiology)

@@

# This figure is a 3 panel figure faceted by strain in columns and O2 in rows. Too stretched.
# Fits are added that are not sig different individually,  next add fits that were sig different dynamically
```{r Plot fits, fig.height= 20, fig.width= 20 }

# scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }
# 
# 
# MED4PURFITPlot <- AllFitsCombined |>
#     filter(Strain == "MED4") |>
#   unnest(cols = c(Data_all), names_sep = "_", keep_empty = TRUE) |>
#   mutate(PhotoperiodLabelTitle = "Photoperiod (h)",
#          OxygenLabel = "Oxygen Concentration (µM)",
#          Photoperiod = factor(Data_all_Photoperiod, levels = c(16, 12, 8, 4)),
#          O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
#          WL = factor(Data_all_WL, levels = c("WW", 660, 450))) %>%
#   ggplot() +
#   geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 4, alpha = 1.0) +
#     geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 2, alpha = 0.8) +
#   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 1, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "MED4")) + 
#    geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "dotted", data = . %>% unnest(Predict_8) %>%  filter(O2_uM != 2.5, Strain == "MED4")) +
#    geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "aa", data = . %>% unnest(Predict_4) %>%  filter(O2_uM != 2.5, Strain == "MED4")) +
#  geom_text(aes(x = 1000, y = 0.75, label= "A     MED4 HLI"), data = . %>% filter(O2_uM == 250, Strain == "MED4"), size = 4, hjust = 0, vjust = 0) +
#   scale_x_continuous(label=scientific_10) +
#    scale_y_continuous(breaks = c(0,0.25, 0.5, 0.75, 1.0), limits = c (0, 1.05)) +
#   scale_colour_manual(values = MCMIXColours, labels = c("White LED", 660, 450)) +
#   scale_linetype_manual(values = MyLineTypes, labels = c("16 hr", "12 hr", "8 hr", "4 hr")) +
#    scale_shape_manual(values = PhotoperiodShapes)  +
#   ggh4x::facet_nested(rows = vars(OxygenLabel, O2_uM), 
#                     labeller = labeller(Strain = label_both, O2_uM = label_value, OxygenLabel = label_value)) +
#  guides(linetype = guide_legend(nrow = 1),
#         fill = "none",
#   theme_bw() +
#    theme( strip.text = element_text(size = 10),
#         axis.title.y = element_blank(),
#         axis.title.x.bottom = element_blank(),
#         axis.text.x = element_blank(),
#         axis.text.y = element_text(size = 9, color = "black", angle = 0, hjust = 1.0),
#         # strip.background=element_rect(fill = "white"),
#         legend.key.size = unit(1, 'cm'), #change legend key size
#         legend.key.height = unit(1, 'cm'), #change legend key height
#         legend.key.width = unit(0.5, 'cm'), #change legend key width
#         legend.title =  element_text(size = 15),  #change legend title font size
#         legend.text = element_text(size = 15),   #change legend text font size
#         legend.position = "top") +
#   labs( shape = "Photoperiod (h)",
#         color = "Growth Waveband (nm)",
#        linetype = "Photoperiod lines"
#       )
# MED4PURFITPlot
# 
# SS120PURFITPlot <- AllFitsCombined |>
#     filter(Strain == "SS120") |>
#   unnest(cols = c(Data_all), names_sep = "_", keep_empty = TRUE) |>
#   mutate(PhotoperiodLabelTitle = "Photoperiod (h)",
#          OxygenLabel = "Oxygen Concentration (µM)",
#          Photoperiod = factor(Data_all_Photoperiod, levels = c(16, 12, 8, 4)),
#          O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
#          WL = factor(Data_all_WL, levels = c("WW", 660, 450))) %>%
#   ggplot() +
#   geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 4, alpha = 1.0) +
#     geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 2, alpha = 0.8) +
#   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 1, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "SS120")) + 
#    geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "dashed", data = . %>% unnest(Predict_12) %>%  filter(O2_uM == 250, Strain == "SS120")) +
#    geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "dotted", data = . %>% unnest(Predict_8) %>%  filter(Strain == "SS120")) +
#    geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "aa", data = . %>% unnest(Predict_4) %>%  filter(Strain == "SS120")) +
#  geom_text(aes(x = 1000, y = 0.75, label= "B     SS120 LLII/III"), data = . %>% filter(O2_uM == 250, Strain == "SS120"), size = 4, hjust = 0, vjust = 0) +
#   scale_x_continuous(label=scientific_10) +
#    scale_y_continuous(breaks = c(0,0.25, 0.5, 0.75, 1.0), limits = c (0, 1.05)) +
#   scale_colour_manual(values = MCMIXColours, labels = c("White LED", 660, 450)) +
#   scale_linetype_manual(values = c("dotdash","dashed", "dotted", "aa"), labels = c("16 hr", "12 hr", "8 hr", "4 hr")) +
#    scale_shape_manual(values = PhotoperiodShapes)  +
#   ggh4x::facet_nested(rows = vars(OxygenLabel, O2_uM), 
#                     labeller = labeller(Strain = label_both, O2_uM = label_value, OxygenLabel = label_value)) +
#  # guides(linetype = guide_legend(nrow = 4),
#  #        fill = "none",
#  #        colour = guide_legend(nrow = 4)) +
#  # guides(shape = guide_legend(nrow = 4)) +
#   theme_bw() +
#    theme( strip.text = element_text(size = 10),
#         axis.title.y = element_blank(),
#         axis.title.x.bottom = element_blank(),
#         axis.text.x = element_blank(),
#         axis.text.y = element_text(size = 10, color = "black", angle = 0, hjust = 1.0),
#         # strip.background=element_rect(fill = "white"),
#         legend.key.size = unit(1, 'cm'), #change legend key size
#         legend.key.height = unit(1, 'cm'), #change legend key height
#         legend.key.width = unit(0.5, 'cm'), #change legend key width
#         # legend.title =  element_text(size = 20),  #change legend title font size
#         # legend.text = element_text(size = 20),   #change legend text font size
#         legend.position = "none") +
#   labs( shape = "Photoperiod (h)",
#         color = "Growth Waveband (nm)",
#        linetype = "Photoperiod (h) "
#       )
#    SS120PURFITPlot
# 
# MIT9313PURFITPlot <- AllFitsCombined |>
#    filter(Strain == "MIT9313") |>
#   unnest(cols = c(Data_all), names_sep = "_", keep_empty = TRUE) |>
#   mutate(PhotoperiodLabelTitle = "Photoperiod (h)",
#          OxygenLabel = "Oxygen Concentration (µM)",
#          Photoperiod = factor(Data_all_Photoperiod, levels = c(16, 12, 8, 4)),
#          O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
#          WL = factor(Data_all_WL, levels = c("WW", 660, 450))) %>%
#   ggplot() +
#   geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 4, alpha = 1.0) +
#     geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 2, alpha = 0.8) +
#   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 1, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "MIT9313")) + 
#   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "dotdash", data = . %>% unnest(Predict_16) %>%  filter(O2_uM == 2.5, Strain == "MIT9313")) +
#    geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "dashed", data = . %>% unnest(Predict_12) %>%  filter(O2_uM != 2.5, Strain == "MIT9313")) +
#    geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "dotted", data = . %>% unnest(Predict_8) %>%  filter(O2_uM == 25, Strain == "MIT9313")) +
#    geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "aa", data = . %>% unnest(Predict_4) %>%  filter(Strain == "MIT9313")) +
#   labs(x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +
#  geom_text(aes(x = 1000, y = 0.75, label= "C     MIT9313 LLIV"), data = . %>% filter(O2_uM == 250, Strain == "MIT9313"), size = 4, hjust = 0, vjust = 0) +
#   scale_x_continuous(breaks = c(0, 1000000,2000000, 3000000, 4000000),label=scientific_10, limits = c (-100, 5000000)) +
#    scale_y_continuous(breaks = c(0, 0.25, 0.5, 0.75, 1.0), limits = c (0, 1.05)) +
#   scale_colour_manual(values = MCMIXColours, labels = c("White LED", 660, 450)) +
#   scale_linetype_manual(values = c("solid","dotdash","dashed", "dotted", "aa"), labels = c("Pooled","16 hr", "12 hr", "8 hr", "4 hr")) +
#    scale_shape_manual(values = PhotoperiodShapes)  +
#   ggh4x::facet_nested(rows = vars(OxygenLabel, O2_uM), 
#                     labeller = labeller(Strain = label_both, WL = label_both, O2_uM = label_value, OxygenLabel = label_value)) +
#  guides(linetype = guide_legend(nrow = 4),
#         fill = "none",
#         colour = guide_legend(nrow = 4)) +
#  guides(shape = guide_legend(nrow = 4)) +
#   theme_bw() +
#    theme( strip.text = element_text(size = 10),
#           axis.title.y = element_blank(),
#           axis.title.x = element_text(size = 15, color = "black"),
#           axis.text.x = element_text(size = 10, color = "black", angle = 0, hjust = 1.0),
#           axis.text.y = element_text(size = 10, color = "black", angle = 0, hjust = 1.0),
#         # strip.background=element_rect(fill = "white"),
#         legend.key.size = unit(1, 'cm'), #change legend key size
#         legend.key.height = unit(1, 'cm'), #change legend key height
#         legend.key.width = unit(0.5, 'cm'), #change legend key width
#         # legend.title =  element_text(size = 20),  #change legend title font size
#         # legend.text = element_text(size = 20),   #change legend text font size
#         legend.position = "none") +
#   labs( shape = "Photoperiod (h)",
#         color = "Growth Waveband (nm)",
#        linetype = "Photoperiod (h) "
#       )
# MIT9313PURFITPlot

# Combine the 3 strains into 1 plot 
```{r combine plots}

# PhotoperiodPurFitsPlots <- plot_grid(MED4PURFITPlot, SS120PURFITPlot, MIT9313PURFITPlot, ncol = 1)
# 
# #create common x and y labels
# y.grob <- textGrob("Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")",
#                    gp = gpar(col="black", fontsize = 15), rot = 90)
# 
# #add to plot
# PhotoperiodPurFitsPlots <- grid.arrange(arrangeGrob(PhotoperiodPurFitsPlots, left = y.grob))

```{r Pur plot strain faceted in columns, fig.height=10, fig.width=10}

@@

# This labels each pane with a letter but turns of the dacet labels
# PhotoperiodPurFitsPlots <- tag_facet(PhotoperiodPurFitsPlots, open = "", close = "", tag_pool = LETTERS, size = 8)
# 
# PhotoperiodPurFitsPlots
```

@@

# AllFitsCombinedWL |>
#   unnest(cols = c(Data_all), names_sep = "_", keep_empty = TRUE) |>
#   mutate(PhotoperiodLabelTitle = "Photoperiod (h)",
#          OxygenLabel = "Oxygen Concentration (µM)",
#          Photoperiod = factor(Data_all_Photoperiod, levels = c(16, 12, 8, 4)),
#          O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
#          WL = factor(Data_all_WL, levels = c("WW", 660, 450)),
#          Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313"))) %>%
#   ggplot() +
#   geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 2, alpha = 0.7) +
#     geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 1.0, alpha = 0.5) +
#   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 1.0, alpha = 0.3, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "MED4")) + 
#    geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6, data = . %>% unnest(Predict_450) %>%  filter(O2_uM == 2.5, Strain == "MED4",  WL == 450)) +
#   geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6, data = . %>% unnest(Predict_660) %>%  filter(Strain == "MED4", WL == 660))+
#     geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6, data = . %>% unnest(Predict_WW) %>%  filter(Strain == "MED4", WL == "WW")) +
#    geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 1.0, alpha = 0.3, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "SS120")) +
#    geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6,  data = . %>% unnest(Predict_450) %>%  filter(Strain == "SS120", O2_uM != 25, WL == 450)) +
#  geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6,  data = . %>% unnest(Predict_WW) %>%  filter(Strain == "SS120", O2_uM != 250, WL == "WW")) +
#    geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 1.0, alpha = 0.3, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "MIT9313")) +
#   geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6, data = . %>% unnest(Predict_660) %>%  filter(Strain == "MIT9313", O2_uM != 250, WL == 660))+
#   geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6,  data = . %>% unnest(Predict_WW) %>%  filter(Strain == "MIT9313", O2_uM == 2.5, WL == "WW")) +
#  labs(title = "Anova fit comparisons of WL to pooled", y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +
#   scale_x_continuous(label=scientific_10) +
#   scale_y_continuous(breaks = c(0,0.25, 0.5, 0.75, 1.0), limits = c (0, 1.05)) +
#   scale_colour_manual(values = MCMIXColours, labels = c("White LED", 660, 450)) +
#   # scale_linetype_manual(values = MyLineTypes, labels = c("16 hr", "12 hr", "8 hr", "4 hr")) +
#   scale_shape_manual(values = PhotoperiodShapes)  +
#   ggh4x::facet_nested(rows = vars(OxygenLabel, O2_uM), cols = vars(Strain), 
#                     labeller = labeller(Strain = label_value, O2_uM = label_value, OxygenLabel = label_value)) +
#  guides(linetype = guide_legend(nrow = 1),
#         fill = "none",
#   theme_bw() +
#    theme( strip.text = element_text(size = 25),
#         axis.title.y = element_text(color = "black", size = 30,  hjust = 0.40),
#         axis.title.x = element_text(color = "black", size = 30),
#         axis.text.x = element_text(size = 20, color = "black", angle = 45, hjust = 1.0),
#         axis.text.y = element_text(size = 20, color = "black", angle = 0, hjust = 1.0),
#         # strip.background=element_rect(color="grey87", fill = "grey82"),
#         # strip.background=element_rect(fill = "white"), 
#         legend.key.size = unit(0.1, 'cm'), #change legend key size
#         legend.key.height = unit(0.1, 'cm'), #change legend key height
#         legend.key.width = unit(0.1, 'cm'), #change legend key width
#         legend.title =  element_text(size = 25),  #change legend title font size
#         legend.text = element_text(size = 25),   #change legend text font size
#         legend.position = "top") +
#   labs( shape = "Photoperiod (h)",
#         color = "Growth Waveband (nm)",
#        linetype = "Photoperiod lines"
#       )

>>>>

```{r load libraries, include=FALSE}
# libraries; Note check actual dependencies
library(tidyverse)
library(lubridate)
library(broom)
library(knitr)
library(zoo)
library(grid)
library(gridExtra)
library(egg)
library(photobiology)
library(minpack.lm)

@@

@@

# Fits are added that are not sig different individually,  next add fits that were sig different dynamically
```{r Pur plot strain faceted in columns, fig.height=10, fig.width=10}

@@

@@
